---
title: "`gramr`: The grammar of grammar"
author: 'Jasmine Dumas (jasmine.dumas@gmail.com)'
date: '2017-05-26'
output:
  html_document: default
  md_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

**Package Developers**: Jasmine Dumas (jasmine.dumas@gmail.com, Ben Marwick (benamrwick@gmail.com), Gordon Shotwell (g.e.shotwell@gmail.com)

The idea behind this package was to develop a tool that checks for common grammatical errors as a companion to the native RStudio spell check, posed in the [ropensci/unconf issue #53](https://github.com/ropensci/unconf17/issues/53). The initial problem statement was to alieviate the time consuming efforts in editing RMarkdown documents in external word processing tools such as MS word or Google sheets and maintain a in-RStudio workflow. 

[paragraph on development approaches and roadblocks encountered]

[paragraph on how the package works]

[paragraph on how we collaborated]

### Example Usage

```{r}
library(gramr)
write_good_file("tests/testthat/test.Rmd")
```

